### 2018-04-04 paper.Rmd
closed #7

abstract: |
  The Child Language Data Exchange System (CHILDES) has played a critical role in research on child language development. However, traditional methods of inquiry into the data have often relied on a command line interface to extract developmental indices or custom parsers to extract data for computational modeling. Now, advances in open-source software allow for novel approaches in working with this dataset. We introduce childes-db, a tool that improves data accessibility and usability by offering novel interfaces to CHILDES, including browsable web applications and an R application programming interface.  Along with a versioned infrastructure that facilitates reproduction of past analyses, these interfaces lower barriers to analyzing naturalistic parent-child language, allowing for a wider range of researchers in language and cognitive development to easily leverage “data from beyond the lab” in their work.

@@

This practice is problematic for a number of reasons. Effort wasted in rewriting the same parser again and again. In addition, this process introduces a major source of errors and inconsistencies in data handling due to difficulties dealing with the many special cases in the CHAT standard. Further, these scripta are rarely shared, leading to much greater difficulty in reproducing the exact numerical results from papers using CHILDES [see e.g., @meylan2017]. This lack of computational reproducibility is widely recognized as problematic because it does not allow researchers to verify or build on published researcher [@donoho2010;@stodden2016]. Finally, the CHILDES corpus itself is a moving target;  computational work using the entire corpus at one time point may include a different set of data than subsequent work (due to new contributions or revisions).

>>>>

abstract: |
  The Child Language Data Exchange System (CHILDES) has played a critical role in research on child language development. However, traditional methods of inquiry into the data have often relied on a command line interface to extract developmental indices or custom parsers to extract data for computational modeling. Now, advances in open-source software allow for novel approaches in working with this dataset. We introduce childes-db, a tool that improves data accessibility and usability by offering novel interfaces to CHILDES, including browsable web applications and an R application programming interface.  Along with a versioned infrastructure that facilitates reproduction of past analyses, these interfaces lower barriers to analyzing naturalistic parent-child language, allowing for a wider range of researchers in language and cognitive development to easily leverage CHILDES in their work.

@@

This practice is problematic for a number of reasons. Effort wasted in rewriting the same parser again and again. In addition, this process introduces a major source of errors and inconsistencies in data handling due to difficulties dealing with the many special cases in the CHAT standard. Further, these scripts are rarely shared, leading to much greater difficulty in reproducing the exact numerical results from papers using CHILDES [see e.g., @meylan2017]. This lack of computational reproducibility is widely recognized as problematic because it does not allow researchers to verify or build on published researcher [@donoho2010;@stodden2016]. Finally, the CHILDES corpus itself is a moving target;  computational work using the entire corpus at one time point may include a different set of data than subsequent work (due to new contributions or revisions).
